\chapter*{Acknowledgments}

I would like to thank my advisor Igor Gornyi for giving me the chance work in a project that has been exciting from day one. The right mixture of giving me freedom in my work and challenging me many times has made this year a very instructive time. I would like to thank him especially for giving me the opportunity to visit Anton Akhmerovs group in Delft -- I had a great time learning \texttt{kwant} from expert people.

I would also like to thank Prof.~Mirlin for agreeing to be my second advisor. 

I thank Anton Akhmerov for giving me the opportunity to visit his group in Delft and for offering me support. A big thank you goes to Muhammad Irfan, who gave me access to his work on SNS junctions and worked together with me showing a lot of patience. 

I also thank Romain Danneau and Rainer Kraft, whose enthusiasm about Quantum Point Contacts and graphene has spread to me. I particularly thank Rainer, who was a great sparring partner when discussing the experiments.

A heartfelt thank you goes to Julia Link and Mareike Hoyer, for proofreading parts of this thesis and, more importantly, always offering support and help in form of advice, chocolate and playing a round of Skat. 

I would like to thank Christian Schramm for being there when I needed him most. I also thank him for proofreading this thesis over and over again, for reminding me to use articles in front of nouns, and for trying to explain me the English punctuation rules to the bitter end.

En \"onemli ve en de\u{g}erli varli\u{g}im benim ailem. Anne, Baba, Yekta -- sonsuz sevginiz ve deste\u{g}iniz i\c{c}in cok tesekk\"ur ederim. 


 

